Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-09 manuscript/manuscript.Rmd
more msy

The MSY rule fixes the drawback in the escapement policy by having $h(F)>0$ for all $F>0$.

>>>>

The MSY rule fixes the drawback in the escapement policy by having $h(F)>0$ for all $F>0$.
It, however, has its own drawbacks.
It is particularly sensitive to misestimates of the parameter $r$, as we will discuss in Sec. \ref{sec:tbd}.
Due to this, similar but more conservative policies have been used.

*Total allowable catch (TAC)* is one such policy.
It consists on reducing the inclination of the line defined by $h(F)$, for example using $h(F) = 0.8\times r/2$.
